---
title: "Simulation Results"
output: 
  html_document:
    toc: true
    number_sections: false
    toc_float: true
    code_folding: hide
editor_options: 
  chunk_output_type: console
date: '2022-05-27'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
.libPaths("C:/Program Files/R/R-4.2.0/library")
.libPaths("C:/Program Files/R/R-4.2.0/library")
library(sjstats)
library(pwr)
library(tidyverse)
library(knitr)
library(kableExtra)
library(wesanderson)
rm(list = ls())
load("sim_results.RData")
results <- 
  results %>% 
  mutate(method = recode(method, 
                         "OLS" = "OLS-CRVE",
                         "FE" = "FE-CRVE"),
         method = factor(method, levels = c("CCREM", "OLS-CRVE", "FE-CRVE")),
         beta = as.factor(gamma100),
         H = as.factor(H),
         J_f = recode(J, "30" = "Students per school = 30",
                         "100" = "Students per school = 100"),
         J_f = factor(J_f, levels = c("Students per school = 30", 
                                      "Students per school = 100")),
         ICC_h = as.factor(ICC_h))

results_assump <- 
  results %>% 
  filter(assumption %in% c("met", "heterosced", "exogeneity")) %>% 
  mutate(assumption = recode(assumption,
                              "met" = "Assumptions met",
                              "heterosced" = "Homoscedasticity violated",
                              "exogeneity" = "Exogeneity violated"),
         assumption = factor(assumption, 
                             levels = c("Assumptions met", 
                                        "Homoscedasticity violated", 
                                        "Exogeneity violated")))

X <- results_assump %>% filter(cov == "X")
W <- results_assump %>% filter(cov == "W")

# ANOVA functions ---------------------------------------------------------------
fml <- " ~ as.factor(method)+as.factor(beta)+as.factor(H)+as.factor(J)+as.factor(ICC_h)+
        as.factor(method)*(as.factor(beta)+as.factor(H)+as.factor(J)+as.factor(ICC_h))+
        as.factor(beta)*(as.factor(H)+as.factor(J)+as.factor(ICC_h))+
        as.factor(H)*(as.factor(J)+as.factor(ICC_h))+
        as.factor(J)*(as.factor(ICC_h))"

tidy_func <- function(obj){
  anova_stats(obj) %>% as_tibble %>% 
    select(term, partial.etasq) %>% 
    mutate(size = ifelse(partial.etasq >= 0.14, "large", NA),
           size = ifelse(partial.etasq >= 0.06 & partial.etasq < 0.14, "medium", size),
           size = ifelse(partial.etasq >= 0.01 & partial.etasq < 0.06, "small", size)) %>% 
    mutate_if(is.numeric, round, 3)
}

table_anova <- function(outcome, cov){
  fit1 <- aov(as.formula(paste0(outcome, fml)), data = cov %>% filter(assumption == "Assumptions met"))
  fit1 <- tidy_func(fit1)
  
  fit2 <- aov(as.formula(paste0(outcome, fml)), data = cov %>% filter(assumption == "Homoscedasticity violated"))
  fit2 <- tidy_func(fit2)
  
  fit3 <- aov(as.formula(paste0(outcome, fml)), data = cov %>% filter(assumption == "Exogeneity violated"))
  fit3 <- tidy_func(fit3)
  
  options(knitr.kable.NA = '')
  fit1 %>% left_join(fit2, by = "term") %>% 
    left_join(fit3, by = "term") %>% filter(term != "Residuals") %>% 
    kable(digits = 4, col.names = c("", rep(c("partial_eta_sq", "size"), 3))) %>% 
    kable_styling(full_width = F) %>% 
    add_header_above(c(" " = 1, "Assumptions met" = 2, "heterosced" = 2, "exogeneity" = 2)) %>% 
    scroll_box(height = "255px")
}
```

# 1. Level-1 covariate (updated)

## Parameter Bias
**Table S5.2**
```{r}
# Table S5.2---------------------------------------------------------------
table_anova("bias", X)
```

**Figure 1**

*Parameter bias of the coefficient estimates of level-1 covariate using CCREM, two-way OLS-CRVE, and two-way FE-CRVE when exogeneity assumption is violated.*
```{r}
# Figure 1
fig1_bias <- X %>%
  filter(assumption == "Exogeneity violated") %>% 
  ggplot(aes(x = H, y = bias, fill = method, color = method)) + 
  geom_boxplot(alpha = .6, lwd = .1) + 
  facet_grid(J_f ~ paste0("School IUCC = ", ICC_h), 
             scales = "free_y") +  
  labs(x = "Number of Schools", y = "Parameter Bias") + 
  theme_bw() +
  theme(text = element_text(size = 10),
        legend.title = element_blank(),
        legend.position = "bottom",
        plot.caption=element_text(hjust = 0),
        axis.text.x = element_text(angle=90, hjust=1)) +
  scale_x_discrete(limits=c("20","70","150")) +
  scale_y_continuous(limits = c(0, .005)) +
  scale_fill_manual(values = c("#FF0000", "#00A08A", "#046C9A")) +
  scale_color_manual(values = c("#FF0000", "#00A08A", "#046C9A"))
fig1_bias
```

*Note*. Neighborhood IUCC is fixed at 0.05.

## Root Mean Squared Error
**Table S5.3**
```{r}
# Table S5.3---------------------------------------------------------------
table_anova("rmse", X)
```

**Figure2**

*RMSE of the coefficient estimates of level-1 covariate using CCREM, two-way OLS-CRVE and two-way FE-CRVE for each assumption scenarios.*
```{r}
# Figure 2----------------------------------------------------------------
fig2_rmse <- X %>%
  group_by(gamma100, gamma010, gamma002, H, G, ICC_h, J, assumption) %>% 
  mutate(rmse_std = 100*rmse/rmse[method == "CCREM"]) %>% 
  ggplot(aes(x = H, y = rmse_std, fill = method, color = method)) + 
  geom_boxplot(alpha = .6, lwd = .1) + 
  facet_grid(assumption ~ paste0("IUCC = ", ICC_h), scales = "free_y") + 
  labs(x = "Number of Schools", y = "Root Mean Squared Error (Standardized)") + 
  theme_bw() +
  theme(text = element_text(size = 10),
        legend.title = element_blank(),
        legend.position = "bottom",
        plot.caption=element_text(hjust = 0),
        axis.text.x = element_text(angle=90, hjust=1)) +
  scale_x_discrete(limits=c("20","70","150")) +
  scale_y_continuous(limits = c(50, 550)) +
  scale_fill_manual(values = c("#FF0000", "#00A08A", "#046C9A")) +
  scale_color_manual(values = c("#FF0000", "#00A08A", "#046C9A"))
fig2_rmse
```

*Note*. Neighborhood IUCC is fixed at 0.05.

## Type I Error Rate
**Table S5.4**
```{r}
# Table S5.4---------------------------------------------------------------
table_anova("rej_rate", X)
```

**Figure 3**

*Type I error rate of the coefficient estimates of level-1 covariate using CCREM, two-way OLS-CRVE and two-way FE-CRVE for each assumption scenarios.*
```{r}
# Figure 3----------------------------------------------------------------
fig3_rej <- X %>%
  ggplot(aes(x = H, y = rej_rate, fill = method, color = method)) + 
  geom_hline(yintercept = .05, linetype = "dashed") +
  geom_boxplot(alpha = .6, lwd = .1) + 
  facet_grid(assumption ~ paste0("IUCC = ", ICC_h), scales = "free_y") + 
  labs(x = "Number of Schools", y = "Type I error rate") + 
  theme_bw() +
  theme(text = element_text(size = 10),
        legend.title = element_blank(),
        legend.position = "bottom",
        plot.caption=element_text(hjust = 0),
        axis.text.x = element_text(angle=90, hjust=1)) +
  scale_x_discrete(limits=c("20","70","150")) +
  # scale_y_continuous(limits = c(0, 1)) +
  scale_fill_manual(values = c("#FF0000", "#00A08A", "#046C9A")) +
  scale_color_manual(values = c("#FF0000", "#00A08A", "#046C9A"))
fig3_rej
```

*Note*. Neighborhood IUCC is fixed at 0.05.

## Confidence Interval Coverage
**Table S5.6**
```{r}
# Table S5.6---------------------------------------------------------------
table_anova("coverage", X)
```

**Figure 4**

*Type I error rate of the coefficient estimates of level-1 covariate using CCREM, two-way OLS-CRVE and two-way FE-CRVE for each assumption scenarios.*
```{r}
# Figure 4----------------------------------------------------------------
fig4_cov <- X %>%
  ggplot(aes(x = H, y = coverage, fill = method, color = method)) + 
  geom_hline(yintercept = c(.925, .975), linetype = "dashed") +
  geom_hline(yintercept = c(.95)) +
  geom_boxplot(alpha = .6, lwd = .1) + 
  facet_grid(assumption ~ paste0("IUCC = ", ICC_h), scales = "free_y") + 
  labs(x = "Number of Schools", y = "Coverage") + 
  theme_bw() +
  theme(text = element_text(size = 10),
        legend.title = element_blank(),
        legend.position = "bottom",
        plot.caption=element_text(hjust = 0),
        axis.text.x = element_text(angle=90, hjust=1)) +
  scale_x_discrete(limits=c("20","70","150")) +
  # scale_y_continuous(limits = c(0, 1)) +
  scale_fill_manual(values = c("#FF0000", "#00A08A", "#046C9A")) +
  scale_color_manual(values = c("#FF0000", "#00A08A", "#046C9A"))
fig4_cov
```

*Note*. Neighborhood IUCC is fixed at 0.05.

# 2. Level-2 covariate

## Parameter Bias
**Table SXX**

```{r}
table_anova("bias", W)
```

**Figure X** 

*Parameter bias of the coefficient estimates of level-2 covariate using CCREM, two-way OLS-CRVE, and two-way FE-CRVE when exogeneity assumption is violated.*
```{r}
fig1_bias <- W %>%
  ggplot(aes(x = H, y = bias, fill = method, color = method)) + 
  geom_boxplot(alpha = .6, lwd = .1) + 
  facet_grid(assumption ~ paste0("School IUCC = ", ICC_h), 
             scales = "free_y") +  
  labs(x = "Number of Schools", y = "Parameter Bias") + 
  theme_bw() +
  theme(text = element_text(size = 10),
        legend.title = element_blank(),
        legend.position = "bottom",
        plot.caption=element_text(hjust = 0),
        axis.text.x = element_text(angle=90, hjust=1)) +
  scale_x_discrete(limits=c("20","70","150")) +
  scale_y_continuous(limits = c(0, .004)) +
  scale_fill_manual(values = c("#FF0000", "#00A08A", "#046C9A")) +
  scale_color_manual(values = c("#FF0000", "#00A08A", "#046C9A"))
fig1_bias
```

*Note*. Neighborhood IUCC is fixed at 0.05.

## Root Mean Squared Error
**Table SXX**
```{r}
# Table SXX---------------------------------------------------------------
table_anova("rmse", W)
```

**Figure2**

*RMSE of the coefficient estimates of level-2 covariate using CCREM, two-way OLS-CRVE and two-way FE-CRVE for each assumption scenarios.*
```{r}
# Figure 2----------------------------------------------------------------
fig2_rmse <- W %>% 
  group_by(gamma100, gamma010, gamma002, H, G, ICC_h, J, assumption) %>% 
  mutate(rmse_std = 100*rmse/rmse[method == "CCREM"]) %>% 
  ggplot(aes(x = H, y = rmse_std, fill = method, color = method)) + 
  geom_boxplot(alpha = .6, lwd = .1) + 
  facet_grid(assumption ~ paste0("IUCC = ", ICC_h), scales = "free_y") + 
  labs(x = "Number of Schools", y = "Root Mean Squared Error (Standardized)") + 
  theme_bw() +
  theme(text = element_text(size = 10),
        legend.title = element_blank(),
        legend.position = "bottom",
        plot.caption=element_text(hjust = 0),
        axis.text.x = element_text(angle=90, hjust=1)) +
  scale_x_discrete(limits=c("20","70","150")) +
  scale_y_continuous(limits = c(50, 200)) +
  scale_fill_manual(values = c("#FF0000", "#00A08A", "#046C9A")) +
  scale_color_manual(values = c("#FF0000", "#00A08A", "#046C9A"))
fig2_rmse
```

*Note*. Neighborhood IUCC is fixed at 0.05.

## Type I Error Rate
**Table SXX**
```{r}
# Table SXX---------------------------------------------------------------
table_anova("rej_rate", W)
```

**Figure 3**

*Type I error rate of the coefficient estimates of level-2 covariate using CCREM, two-way OLS-CRVE and two-way FE-CRVE for each assumption scenarios.*
```{r}
# Figure 3----------------------------------------------------------------
fig3_rej <- W %>% 
  ggplot(aes(x = H, y = rej_rate, fill = method, color = method)) + 
  geom_hline(yintercept = .05, linetype = "dashed") +
  geom_boxplot(alpha = .6, lwd = .1) + 
  facet_grid(assumption ~ paste0("IUCC = ", ICC_h), scales = "free_y") + 
  labs(x = "Number of Schools", y = "Type I error rate") + 
  theme_bw() +
  theme(text = element_text(size = 10),
        legend.title = element_blank(),
        legend.position = "bottom",
        plot.caption=element_text(hjust = 0),
        axis.text.x = element_text(angle=90, hjust=1)) +
  scale_x_discrete(limits=c("20","70","150")) +
  # scale_y_continuous(limits = c(0, 1)) +
  scale_fill_manual(values = c("#FF0000", "#00A08A", "#046C9A")) +
  scale_color_manual(values = c("#FF0000", "#00A08A", "#046C9A"))
fig3_rej
```

*Note*. Neighborhood IUCC is fixed at 0.05.

## Confidence Interval Coverage
**Table SXX**
```{r}
# Table SXX---------------------------------------------------------------
table_anova("coverage", W)
```

**Figure 4**

*Type I error rate of the coefficient estimates of level-2 covariate using CCREM, two-way OLS-CRVE and two-way FE-CRVE for each assumption scenarios.*
```{r}
# Figure 4----------------------------------------------------------------
fig4_cov <- W %>% 
  ggplot(aes(x = H, y = coverage, fill = method, color = method)) + 
  geom_hline(yintercept = c(.925, .975), linetype = "dashed") +
  geom_hline(yintercept = c(.95)) +
  geom_boxplot(alpha = .6, lwd = .1) + 
  facet_grid(assumption ~ paste0("IUCC = ", ICC_h), scales = "free_y") + 
  labs(x = "Number of Schools", y = "Coverage") + 
  theme_bw() +
  theme(text = element_text(size = 10),
        legend.title = element_blank(),
        legend.position = "bottom",
        plot.caption=element_text(hjust = 0),
        axis.text.x = element_text(angle=90, hjust=1)) +
  scale_x_discrete(limits=c("20","70","150")) +
  # scale_y_continuous(limits = c(0, 1)) +
  scale_fill_manual(values = c("#FF0000", "#00A08A", "#046C9A")) +
  scale_color_manual(values = c("#FF0000", "#00A08A", "#046C9A"))
fig4_cov
```

*Note*. Neighborhood IUCC is fixed at 0.05.

# 3. Random slope
```{r}
results_rs <- results %>% 
  filter(assumption %in% c("met", "random slopes")) %>% 
  mutate(J = as.factor(J),
         assumption = recode(assumption,
                             "met" = "Correctly Specified", 
                             "random slopes" = "Misspecified"),
         assumption = factor(assumption, 
                             levels = c("Correctly Specified", "Misspecified")))

X <- results_rs %>% filter(cov == "X")
W <- results_rs %>% filter(cov == "W")

table_anova <- function(outcome, cov){
  fit1 <- aov(as.formula(paste0(outcome, fml)), data = cov %>% filter(assumption == "Correctly Specified"))
  fit1 <- tidy_func(fit1)
  
  fit2 <- aov(as.formula(paste0(outcome, fml)), data = cov %>% filter(assumption == "Misspecified"))
  fit2 <- tidy_func(fit2)
  
  options(knitr.kable.NA = '')
  fit1 %>% left_join(fit2, by = "term") %>% 
    filter(term != "Residuals") %>% 
    kable(digits = 4, col.names = c("", rep(c("partial_eta_sq", "size"), 2))) %>% 
    kable_styling(full_width = F) %>% 
    add_header_above(c(" " = 1, "Correctly Specified" = 2, "Misspecified" = 2)) %>% 
    scroll_box(height = "255px")
}
```

## Parameter Bias

**Level-1 covariate**

```{r}
table_anova("bias", X)

fig1_bias <- X %>%
  ggplot(aes(x = J, y = bias, fill = method, color = method)) + 
  geom_boxplot(alpha = .6, lwd = .1) + 
  facet_grid(assumption ~ paste0("School IUCC = ", ICC_h), 
             scales = "free_y") +  
  labs(x = "Students per school", y = "Parameter Bias") + 
  theme_bw() +
  theme(text = element_text(size = 10),
        legend.title = element_blank(),
        legend.position = "bottom",
        plot.caption=element_text(hjust = 0),
        axis.text.x = element_text(angle=90, hjust=1)) +
  scale_x_discrete(limits=c("30","100")) +
  scale_y_continuous(limits = c(0, .003)) +
  scale_fill_manual(values = c("#FF0000", "#00A08A", "#046C9A")) +
  scale_color_manual(values = c("#FF0000", "#00A08A", "#046C9A"))
fig1_bias
```

**Level-2 covariate**

```{r}
table_anova("bias", W)

fig1_bias <- W %>%
  ggplot(aes(x = H, y = bias, fill = method, color = method)) + 
  geom_boxplot(alpha = .6, lwd = .1) + 
  facet_grid(assumption ~ paste0("School IUCC = ", ICC_h), 
             scales = "free_y") +  
  labs(x = "Students per school", y = "Parameter Bias") + 
  theme_bw() +
  theme(text = element_text(size = 10),
        legend.title = element_blank(),
        legend.position = "bottom",
        plot.caption=element_text(hjust = 0),
        axis.text.x = element_text(angle=90, hjust=1)) +
  scale_x_discrete(limits=c("20", "70", "150")) +
  scale_y_continuous(limits = c(-.01, .05)) +
  scale_fill_manual(values = c("#FF0000", "#00A08A", "#046C9A")) +
  scale_color_manual(values = c("#FF0000", "#00A08A", "#046C9A"))
fig1_bias
```

## Root Mean Squared Error
**Level-1 covariate**
```{r}
table_anova("rmse", X)

fig2_rmse <- X %>% 
  group_by(gamma100, gamma010, gamma002, H, G, ICC_h, J, assumption) %>% 
  mutate(rmse_std = 100*rmse/rmse[method == "CCREM"]) %>% 
  ggplot(aes(x = H, y = rmse_std, fill = method, color = method)) + 
  geom_boxplot(alpha = .6, lwd = .1) + 
  facet_grid(assumption ~ paste0("IUCC = ", ICC_h), scales = "free_y") + 
  labs(x = "Number of Schools", y = "Root Mean Squared Error (Standardized)") + 
  theme_bw() +
  theme(text = element_text(size = 10),
        legend.title = element_blank(),
        legend.position = "bottom",
        plot.caption=element_text(hjust = 0),
        axis.text.x = element_text(angle=90, hjust=1)) +
  scale_x_discrete(limits=c("20","70","150")) +
  scale_y_continuous(limits = c(50, 200)) +
  scale_fill_manual(values = c("#FF0000", "#00A08A", "#046C9A")) +
  scale_color_manual(values = c("#FF0000", "#00A08A", "#046C9A"))
fig2_rmse
```

**Level-2 covariate**
```{r}
table_anova("rmse", W)

fig2_rmse <- W %>% 
  group_by(gamma100, gamma010, gamma002, H, G, ICC_h, J, assumption) %>% 
  mutate(rmse_std = 100*rmse/rmse[method == "CCREM"]) %>% 
  ggplot(aes(x = H, y = rmse_std, fill = method, color = method)) + 
  geom_boxplot(alpha = .6, lwd = .1) + 
  facet_grid(assumption ~ paste0("IUCC = ", ICC_h), scales = "free_y") + 
  labs(x = "Number of Schools", y = "Root Mean Squared Error (Standardized)") + 
  theme_bw() +
  theme(text = element_text(size = 10),
        legend.title = element_blank(),
        legend.position = "bottom",
        plot.caption=element_text(hjust = 0),
        axis.text.x = element_text(angle=90, hjust=1)) +
  scale_x_discrete(limits=c("20","70","150")) +
  scale_y_continuous(limits = c(50, 200)) +
  scale_fill_manual(values = c("#FF0000", "#00A08A", "#046C9A")) +
  scale_color_manual(values = c("#FF0000", "#00A08A", "#046C9A"))
fig2_rmse
```

## Type I Error Rate
**Level-1 covariate**
```{r}
table_anova("rej_rate", X)

fig3_rej <- X %>% 
  ggplot(aes(x = H, y = rej_rate, fill = method, color = method)) + 
  geom_hline(yintercept = .05, linetype = "dashed") +
  geom_boxplot(alpha = .6, lwd = .1) + 
  facet_grid(assumption ~ paste0("IUCC = ", ICC_h), scales = "free_y") + 
  labs(x = "Number of Schools", y = "Type I error rate") + 
  theme_bw() +
  theme(text = element_text(size = 10),
        legend.title = element_blank(),
        legend.position = "bottom",
        plot.caption=element_text(hjust = 0),
        axis.text.x = element_text(angle=90, hjust=1)) +
  scale_x_discrete(limits=c("20","70","150")) +
  # scale_y_continuous(limits = c(0, 1)) +
  scale_fill_manual(values = c("#FF0000", "#00A08A", "#046C9A")) +
  scale_color_manual(values = c("#FF0000", "#00A08A", "#046C9A"))
fig3_rej
```

**Level-2 covariate**
```{r}
table_anova("rej_rate", W)

fig3_rej <- W %>% 
  ggplot(aes(x = H, y = rej_rate, fill = method, color = method)) + 
  geom_hline(yintercept = .05, linetype = "dashed") +
  geom_boxplot(alpha = .6, lwd = .1) + 
  facet_grid(assumption ~ paste0("IUCC = ", ICC_h), scales = "free_y") + 
  labs(x = "Number of Schools", y = "Type I error rate") + 
  theme_bw() +
  theme(text = element_text(size = 10),
        legend.title = element_blank(),
        legend.position = "bottom",
        plot.caption=element_text(hjust = 0),
        axis.text.x = element_text(angle=90, hjust=1)) +
  scale_x_discrete(limits=c("20","70","150")) +
  # scale_y_continuous(limits = c(0, 1)) +
  scale_fill_manual(values = c("#FF0000", "#00A08A", "#046C9A")) +
  scale_color_manual(values = c("#FF0000", "#00A08A", "#046C9A"))
fig3_rej
```

## Confidence Interval Coverage
**Level-1 covariate**
```{r}
table_anova("coverage", X)

fig4_cov <- X %>% 
  ggplot(aes(x = H, y = coverage, fill = method, color = method)) + 
  geom_hline(yintercept = c(.925, .975), linetype = "dashed") +
  geom_hline(yintercept = c(.95)) +
  geom_boxplot(alpha = .6, lwd = .1) + 
  facet_grid(assumption ~ J_f, scales = "free_y") + 
  labs(x = "Number of Schools", y = "Coverage") + 
  theme_bw() +
  theme(text = element_text(size = 10),
        legend.title = element_blank(),
        legend.position = "bottom",
        plot.caption=element_text(hjust = 0),
        axis.text.x = element_text(angle=90, hjust=1)) +
  scale_x_discrete(limits=c("20","70","150")) +
  # scale_y_continuous(limits = c(0, 1)) +
  scale_fill_manual(values = c("#FF0000", "#00A08A", "#046C9A")) +
  scale_color_manual(values = c("#FF0000", "#00A08A", "#046C9A"))
fig4_cov
```

**Level-2 covariate**
```{r}
table_anova("coverage", W)

fig4_cov <- W %>% 
  ggplot(aes(x = H, y = coverage, fill = method, color = method)) + 
  geom_hline(yintercept = c(.925, .975), linetype = "dashed") +
  geom_hline(yintercept = c(.95)) +
  geom_boxplot(alpha = .6, lwd = .1) + 
  facet_grid(assumption ~ J_f, scales = "free_y") + 
  labs(x = "Number of Schools", y = "Coverage") + 
  theme_bw() +
  theme(text = element_text(size = 10),
        legend.title = element_blank(),
        legend.position = "bottom",
        plot.caption=element_text(hjust = 0),
        axis.text.x = element_text(angle=90, hjust=1)) +
  scale_x_discrete(limits=c("20","70","150")) +
  # scale_y_continuous(limits = c(0, 1)) +
  scale_fill_manual(values = c("#FF0000", "#00A08A", "#046C9A")) +
  scale_color_manual(values = c("#FF0000", "#00A08A", "#046C9A"))
fig4_cov
```
