---
title: "Simulation Results"
subtitle: "Comparing Random Effects Models, Ordinary Least Squares, or Fixed Effects with Cluster Robust Standard Errors for Cross-Classified Data"
author: "Young Ri Lee"
output: 
  html_document:
    toc: true
    number_sections: false
    toc_float: true
    code_folding: hide
editor_options: 
  chunk_output_type: console
date: '2022-05-27'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
.libPaths("C:/Program Files/R/R-4.2.0/library")
.libPaths("C:/Program Files/R/R-4.2.0/library")
library(sjstats)
library(pwr)
library(tidyverse)
library(knitr)
library(kableExtra)
library(wesanderson)
rm(list = ls())
load("sim_results.RData")
results <- 
  results %>% 
  mutate(method = recode(method, "OLS" = "OLS-CRVE", "FE" = "FE-CRVE"),
         method = factor(method, levels = c("CCREM", "OLS-CRVE", "FE-CRVE")),
         beta = as.factor(gamma100),
         H = as.factor(H),
         J_f = recode(J, "30" = "Students per school = 30",
                         "100" = "Students per school = 100"),
         J_f = factor(J_f, levels = c("Students per school = 30", 
                                      "Students per school = 100")),
         ICC_h = as.factor(ICC_h), 
         assumption = recode(assumption,
                             "met" = "Assumptions met",
                             "heterosced" = "Homoscedasticity",
                             "exogeneity" = "Exogeneity",
                             "random slopes" = "Random Slopes"),
         assumption = factor(assumption, 
                             levels = c("Assumptions met", 
                                        "Homoscedasticity", 
                                        "Exogeneity",
                                        "Random Slopes")))

X <- results %>% filter(cov == "X") # level-1 cov
W <- results %>% filter(cov == "W") # level-2 cov, neighborhood
Z <- results %>% filter(cov == "Z") # level-2 cov, school

# ANOVA functions ---------------------------------------------------------------
fml <- " ~ as.factor(method)+as.factor(beta)+as.factor(H)+as.factor(J)+as.factor(ICC_h)+
        as.factor(method)*(as.factor(beta)+as.factor(H)+as.factor(J)+as.factor(ICC_h))+
        as.factor(beta)*(as.factor(H)+as.factor(J)+as.factor(ICC_h))+
        as.factor(H)*(as.factor(J)+as.factor(ICC_h))+
        as.factor(J)*(as.factor(ICC_h))"

tidy_func <- function(obj){
  anova_stats(obj) %>% as_tibble %>% 
    select(term, partial.etasq) %>% 
    mutate(size = ifelse(partial.etasq >= 0.14, "large", NA),
           size = ifelse(partial.etasq >= 0.06 & partial.etasq < 0.14, "medium", size),
           size = ifelse(partial.etasq >= 0.01 & partial.etasq < 0.06, "small", size)) %>% 
    mutate_if(is.numeric, round, 3)
}

table_anova <- function(outcome, cov){
  fit1 <- aov(as.formula(paste0(outcome, fml)), 
              data = cov %>% filter(assumption == "Assumptions met"))
  fit1 <- tidy_func(fit1)
  
  fit2 <- aov(as.formula(paste0(outcome, fml)), 
              data = cov %>% filter(assumption == "Homoscedasticity"))
  fit2 <- tidy_func(fit2)
  
  fit3 <- aov(as.formula(paste0(outcome, fml)), 
              data = cov %>% filter(assumption == "Exogeneity"))
  fit3 <- tidy_func(fit3)
  
  fit4 <- aov(as.formula(paste0(outcome, fml)), 
              data = cov %>% filter(assumption == "Random Slopes"))
  fit4 <- tidy_func(fit4)
  
  options(knitr.kable.NA = '')
  fit1 %>% 
    left_join(fit2, by = "term") %>% 
    left_join(fit3, by = "term") %>% 
    left_join(fit4, by = "term") %>% 
    filter(term != "Residuals") %>% 
    mutate(term = c("method", "beta", "Number of Schools (H)", 
                    "Students per School (J)", "ICC_h", "method:beta", 
                    "method:H", "method:J", "method:ICC_h", "beta:H", 
                    "beta:J", "beta:ICC_h", "H:J", "H:ICC_h", "J:ICC_h")) %>% 
    kable(digits = 4, col.names = c("", rep(c("p_eta_sq", "size"), 4))) %>% 
    kable_styling(full_width = F) %>% 
    add_header_above(c(" " = 1, "Assumptions met" = 2, "Heterosced" = 2, 
                       "Exogeneity" = 2, "Random Slopes" = 2)) 
    # scroll_box(height = "255px")
}
```

# 1. Level-1 covariate (updated)

## Parameter Bias
**Table S5.2**
```{r}
# Table S5.2---------------------------------------------------------------
table_anova("bias", X)
```

**Figure 1**

*Parameter bias of the coefficient estimates of level-1 covariate using CCREM, two-way OLS-CRVE, and two-way FE-CRVE for each assumption scenarios.*
```{r}
# Figure 1
fig1_bias <- X %>%
  ggplot(aes(x = H, y = bias, fill = method, color = method)) + 
  geom_boxplot(alpha = .6, lwd = .1) + 
  facet_grid(assumption ~ J_f, scales = "free_y") +  
  labs(x = "Number of Schools", y = "Parameter Bias") + 
  theme_bw() +
  theme(text = element_text(size = 10),
        legend.title = element_blank(),
        legend.position = "bottom",
        plot.caption=element_text(hjust = 0),
        axis.text.x = element_text(angle=90, hjust=1)) +
  scale_x_discrete(limits=c("20","70","150")) +
  scale_y_continuous(limits = c(-.004, .005)) +
  scale_fill_manual(values = c("#FF0000", "#00A08A", "#046C9A")) +
  scale_color_manual(values = c("#FF0000", "#00A08A", "#046C9A"))
fig1_bias
```

*Note*. Neighborhood IUCC is fixed at 0.05.

## Root Mean Squared Error
**Table S5.3**
```{r}
# Table S5.3---------------------------------------------------------------
table_anova("rmse", X)
```

**Figure2**

*RMSE of the coefficient estimates of level-1 covariate using CCREM, two-way OLS-CRVE and two-way FE-CRVE for each assumption scenarios.*
```{r}
# Figure 2----------------------------------------------------------------
fig2_rmse <- X %>%
  group_by(gamma100, gamma010, gamma002, H, G, ICC_h, J, assumption) %>% 
  mutate(rmse_std = 100*rmse/rmse[method == "CCREM"]) %>% 
  ggplot(aes(x = H, y = rmse_std, fill = method, color = method)) + 
  geom_boxplot(alpha = .6, lwd = .1) + 
  facet_grid(assumption ~ J_f, scales = "free_y") + 
  labs(x = "Number of Schools", y = "Root Mean Squared Error (Standardized)") + 
  theme_bw() +
  theme(text = element_text(size = 10),
        legend.title = element_blank(),
        legend.position = "bottom",
        plot.caption=element_text(hjust = 0),
        axis.text.x = element_text(angle=90, hjust=1)) +
  scale_x_discrete(limits=c("20","70","150")) +
  scale_y_continuous(limits = c(40, 260)) +
  scale_fill_manual(values = c("#FF0000", "#00A08A", "#046C9A")) +
  scale_color_manual(values = c("#FF0000", "#00A08A", "#046C9A"))
fig2_rmse
```

*Note*. Neighborhood IUCC is fixed at 0.05.

## Type I Error Rate
**Table S5.4**
```{r}
# Table S5.4---------------------------------------------------------------
table_anova("rej_rate", X)
```

**Figure 3**

*Type I error rate of the coefficient estimates of level-1 covariate using CCREM, two-way OLS-CRVE and two-way FE-CRVE for each assumption scenarios.*
```{r}
# Figure 3----------------------------------------------------------------
fig3_rej <- X %>%
  ggplot(aes(x = H, y = rej_rate, fill = method, color = method)) + 
  geom_hline(yintercept = .05, linetype = "dashed") +
  geom_boxplot(alpha = .6, lwd = .1) + 
  facet_grid(assumption ~ J_f, scales = "free_y") + 
  labs(x = "Number of Schools", y = "Type I error rate") + 
  theme_bw() +
  theme(text = element_text(size = 10),
        legend.title = element_blank(),
        legend.position = "bottom",
        plot.caption=element_text(hjust = 0),
        axis.text.x = element_text(angle=90, hjust=1)) +
  scale_x_discrete(limits=c("20","70","150")) +
  # scale_y_continuous(limits = c(0, 1)) +
  scale_fill_manual(values = c("#FF0000", "#00A08A", "#046C9A")) +
  scale_color_manual(values = c("#FF0000", "#00A08A", "#046C9A"))
fig3_rej
```

*Note*. Neighborhood IUCC is fixed at 0.05.

# 2. Level-2 covariates 

## Parameter Bias
**Neighborhood**
```{r}
table_anova("bias", W)

s6_1_1_bias <- W %>%
  ggplot(aes(x = H, y = bias, fill = method, color = method)) + 
  geom_boxplot(alpha = .6, lwd = .1) + 
  facet_grid(assumption ~ paste0("IUCC = ", ICC_h), 
             scales = "free_y") +  
  labs(x = "Number of Schools", y = "Parameter Bias") + 
  theme_bw() +
  theme(text = element_text(size = 10),
        legend.title = element_blank(),
        legend.position = "bottom",
        plot.caption=element_text(hjust = 0),
        axis.text.x = element_text(angle=90, hjust=1)) +
  scale_x_discrete(limits=c("20","70","150")) +
  scale_y_continuous(limits = c(-.006, .01)) +
  scale_fill_manual(values = c("#FF0000", "#00A08A", "#046C9A")) +
  scale_color_manual(values = c("#FF0000", "#00A08A", "#046C9A"))
s6_1_1_bias
```

**School**
```{r}
table_anova("bias", Z)

s6_1_2_bias <- Z %>%
  ggplot(aes(x = H, y = bias, fill = method, color = method)) + 
  geom_boxplot(alpha = .6, lwd = .1) + 
  facet_grid(assumption ~ paste0("IUCC = ", ICC_h), 
             scales = "free_y") +  
  labs(x = "Number of Schools", y = "Parameter Bias") + 
  theme_bw() +
  theme(text = element_text(size = 10),
        legend.title = element_blank(),
        legend.position = "bottom",
        plot.caption=element_text(hjust = 0),
        axis.text.x = element_text(angle=90, hjust=1)) +
  scale_x_discrete(limits=c("20","70","150")) +
  scale_y_continuous(limits = c(-.015, .01)) +
  scale_fill_manual(values = c("#FF0000", "#00A08A", "#046C9A")) +
  scale_color_manual(values = c("#FF0000", "#00A08A", "#046C9A"))
s6_1_2_bias
```

## Root Mean Squared Error
**Neighborhood**
```{r}
table_anova("rmse", W)

s6_2_1_rmse <- W %>% 
  group_by(gamma100, gamma010, gamma002, H, G, ICC_h, J, assumption) %>% 
  mutate(rmse_std = 100*rmse/rmse[method == "CCREM"]) %>% 
  ggplot(aes(x = H, y = rmse_std, fill = method, color = method)) + 
  geom_boxplot(alpha = .6, lwd = .1) + 
  facet_grid(assumption ~ J_f, scales = "free_y") + 
  labs(x = "Number of Schools", y = "Root Mean Squared Error (Standardized)") + 
  theme_bw() +
  theme(text = element_text(size = 10),
        legend.title = element_blank(),
        legend.position = "bottom",
        plot.caption=element_text(hjust = 0),
        axis.text.x = element_text(angle=90, hjust=1)) +
  scale_x_discrete(limits=c("20","70","150")) +
  scale_y_continuous(limits = c(90, 160)) +
  scale_fill_manual(values = c("#FF0000", "#00A08A", "#046C9A")) +
  scale_color_manual(values = c("#FF0000", "#00A08A", "#046C9A"))
s6_2_1_rmse
```

**School**
```{r}
table_anova("rmse", Z)

s6_2_2_rmse <- Z %>% 
  group_by(gamma100, gamma010, gamma002, H, G, ICC_h, J, assumption) %>% 
  mutate(rmse_std = 100*rmse/rmse[method == "CCREM"]) %>% 
  ggplot(aes(x = H, y = rmse_std, fill = method, color = method)) + 
  geom_boxplot(alpha = .6, lwd = .1) + 
  facet_grid(assumption ~ J_f, scales = "free_y") + 
  labs(x = "Number of Schools", y = "Root Mean Squared Error (Standardized)") + 
  theme_bw() +
  theme(text = element_text(size = 10),
        legend.title = element_blank(),
        legend.position = "bottom",
        plot.caption=element_text(hjust = 0),
        axis.text.x = element_text(angle=90, hjust=1)) +
  scale_x_discrete(limits=c("20","70","150")) +
  scale_y_continuous(limits = c(98, 104)) +
  scale_fill_manual(values = c("#FF0000", "#00A08A", "#046C9A")) +
  scale_color_manual(values = c("#FF0000", "#00A08A", "#046C9A"))
s6_2_2_rmse
```

## Type I Error Rate
**Neighborhood**
```{r}
table_anova("rej_rate", W)

s6_3_1_rej <- W %>% 
  ggplot(aes(x = H, y = rej_rate, fill = method, color = method)) + 
  geom_hline(yintercept = .05, linetype = "dashed") +
  geom_boxplot(alpha = .6, lwd = .1) + 
  facet_grid(assumption ~ J_f, scales = "free_y") + 
  labs(x = "Number of Schools", y = "Type I error rate") + 
  theme_bw() +
  theme(text = element_text(size = 10),
        legend.title = element_blank(),
        legend.position = "bottom",
        plot.caption=element_text(hjust = 0),
        axis.text.x = element_text(angle=90, hjust=1)) +
  scale_x_discrete(limits=c("20","70","150")) +
  scale_y_continuous(limits = c(0.03, .11)) +
  scale_fill_manual(values = c("#FF0000", "#00A08A", "#046C9A")) +
  scale_color_manual(values = c("#FF0000", "#00A08A", "#046C9A"))
s6_3_1_rej
```

**School**
```{r}
table_anova("rej_rate", Z)

s6_3_2_rej <- Z %>% 
  ggplot(aes(x = H, y = rej_rate, fill = method, color = method)) + 
  geom_hline(yintercept = .05, linetype = "dashed") +
  geom_boxplot(alpha = .6, lwd = .1) + 
  facet_grid(assumption ~ J_f, scales = "free_y") + 
  labs(x = "Number of Schools", y = "Type I error rate") + 
  theme_bw() +
  theme(text = element_text(size = 10),
        legend.title = element_blank(),
        legend.position = "bottom",
        plot.caption=element_text(hjust = 0),
        axis.text.x = element_text(angle=90, hjust=1)) +
  scale_x_discrete(limits=c("20","70","150")) +
  # scale_y_continuous(limits = c(0.03, .14)) +
  scale_fill_manual(values = c("#FF0000", "#00A08A", "#046C9A")) +
  scale_color_manual(values = c("#FF0000", "#00A08A", "#046C9A"))
s6_3_2_rej
```
